Identifying regime transitions for water governance: Take the Yellow River Basin in China as case

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
feat(paper): :sparkles: 讨论审稿人提出的变化点问题

\subsection{Comment \#7}
% 讨论:从您对变更点的分析中可以明显看出，每个制度中都存在变更点。但为什么会出现这些变化“点”呢?是什么导致或触发了它们?这是管理机构的变化还是象征性的政策变化?该制度期间的特征已被很好地描述，但请更多地考虑为什么变化点发生在特定的年份/时期。
\RC{} Discussion: The existence of change points in each of the regimes is evident from your analysis of the change points. But why did these change "points" occur? What caused or triggered them? Was it a change in governing institutions or a symbolic policy change? The characteristics during that regime period are well described, but please give more thought to why the change points occurred in that particular year/period.

% 感谢如此有趣的评论，虽然制度在特定的点发生变化，但我们认为总体来说是。这就像复杂系统中不是单独的一个，
\AR{} A good comment.

>>>>

\subsection{Comment \#7}
% 讨论:从您对变更点的分析中可以明显看出，每个制度中都存在变更点。但为什么会出现这些变化“点”呢?是什么导致或触发了它们?这是管理机构的变化还是象征性的政策变化?该制度期间的特征已被很好地描述，但请更多地考虑为什么变化点发生在特定的年份/时期。
\RC{} Discussion: The existence of change points in each of the regimes is evident from your analysis of the change points. But why did these change ``points'' occur? What caused or triggered them? Was it a change in governing institutions or a symbolic policy change? The characteristics during that regime period are well described, but please give more thought to why the change points occurred in that particular year/period.

% 感谢如此有趣的评论，虽然制度在特定的点发生变化，但我们总体认为制度转变还是一段时间内持续、积累的变化在特定的点产生了统计特征，很难将其总结成某种因素造成的变化。这也是为什么我们要把各种因素考虑在内，构造这样一个综合指数的原因，不是吗？
\AR{} Thanks to such interesting comments, although the result changes at certain points statistically, we generally believe that the change of the system is still a result of the accumulation of water governance practices in period of time. Therefore, it is difficult to summarize it into a change caused by one factor. That's why we have to take all these factors into account and construct a composite index like this, right?

% 我们认为这类似于复杂系统的涌现，许多数不胜数的治理措施在不断地提出与执行（正如图3C所示），每一个措施都会针对一个具体的问题，但流域整体将向何处发展取决于这些措施的合力。
\AR*{} We think of this as analogous to the ``emergence'' of complex systems. Numerous practices being proposed and implemented (e.g., basin-scaled practices of the Yellow River as shown in Figure~3C). Each practice addresses a specific issue, but how the water governance feature changing overall depends on a combination of their outcomes.

% 当然，并不是说完全无法在特定年份为Regime shift给出解释。在中国的治理模式里，``领会精神''是一个有趣的东西。通常，中央高层会释放一些信号，各级政府（包括部委和地方行政部门）如果按照这种``精神''执行了某种治理措施并取得不错的成果，便是一个非常好的政绩。这种治理模式便是我们在结果、图3、讨论中都提及``social atmosphere''（返修前的手稿我们称之为 social transformation）的原因，这种治理风气会引导治理措施。
\AR*{} It is not to say that there is absolutely no explanation for Regime shift in a given year. In China's governance model, ``central spirit'' is interesting. Usually, the top level of the central government sends some signals. If governments at all levels (including ministries and local administrative departments) implement certain governance measures in accordance with this ``spirit'' and achieve good results, it will be a good governance. This feature is the reason why we mentioned the ``social atmosphere'' (the manuscript before the revision was called social transformation) in the results, Figure 3, and discussion -atmosphere can guide the governance practices.

% 例如在上世纪1960s到1970s，中国在毛泽东领导下有着强烈的``征服自然''风气，这是非常出名的，这种风气能导致建立更多的水库大坝、增大供给。而改革开放带来的阶段二的需求增加、水竞争、效率提升。2000年后中国强调环境治理，等等。可以说我们识别的两次转变都和``social atmosphere''的变化不无关系。但我们很小心的避免了这种归因，因为这种治理转变，绝非单独自上而下的一句口号就能实现的，也有很多其它类似的``中央精神''未能得到有效贯彻执行。
\AR*{} For instance, the ``reform and opening up'' led to increased water demand, water competition and efficiency in transformation regime. After 2000, China emphasized environmental issues \dots It can be said that the two changes we identified are partially related to the change of ``social atmosphere''. But we are very careful to avoid this simple attribution, because this change in governance can not be achieved by a top-down slogan alone, and there are many other similar ``central spirit'' has not been effectively implemented.

\AR*{} Taken together, we believe regime shifts are ``emergence'' of the human-water system, but the significant and solid changing points of the YRB can be related to social atmosphere.
